Reanalysis Step 6: Sensitivity Analysis and E-values

### 2025-09-01 reanalysis-6-sensitivity.qmd
sensitivity analysis bugs

# Create E-value plot using RR values
# bias_plot expects RR values, not E-values
tryCatch({
  # The bias_plot function expects the RR estimate and its bounds
  bias_plot_obj <- bias_plot(rr_point, rr_lower)
  print(bias_plot_obj)
}, error = function(e) {
  cat("Note: Bias plot could not be generated.\n")
  cat("Error: ", e$message, "\n")
  cat("RR point: ", rr_point, ", RR lower: ", rr_lower, "\n")
})
```

>>>>

# Create E-value plot
# bias_plot expects RR point estimate and x-axis max
tryCatch({
  bias_plot_obj <- bias_plot(rr_point, 10)
  print(bias_plot_obj)
}, error = function(e) {
  cat("Note: Bias plot could not be generated.\n")
  cat("Error: ", e$message, "\n")
})
```
